---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

#title: "Question 2: Yield Spread"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: yes
Entry1: Question 5 - Volatility and GARCH estimates
Entry2: \textbf{Carel Olivier} # textbf for bold
Entry3: 22017542
Uni_Logo: Tex/garch.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
#Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |

---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')

if(!require("tidyverse")) install.packages("tidyverse")

pacman::p_load("MTS", "robustbase")

pacman::p_load("tidyverse", "devtools", "rugarch", "rmgarch", 
     "forecast", "tbl2xts", "lubridate", "PerformanceAnalytics", 
     "ggthemes", "dplyr", "cowplot", "fmxdat") 

list.files('C:/Users/Cabous/OneDrive/Desktop/22017542_Exam/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```


# Short Introduction

The study of volatility is particularly important in financial modelling. Thus, in this question I will look at the South African ZAR since it has been quite volatile over the past couple of years. More specifically, I will conduct a simple univariate-GARCH estimation to analyse the volatility of the Rand.


```{r}
# Load Data

cncy <- read_rds("data/currencies.rds")

cncy_Carry <- read_rds("data/cncy_Carry.rds")

cncy_value <- read_rds("data/cncy_value.rds")

cncyIV <- read_rds("data/cncyIV.rds")

bbdxy <- read_rds("data/bbdxy.rds")

```


# Implied Volatility

I will start by looking at implied volatility. The market's estimate of how much a currency pair will fluctuate over a certain period in the future is known as implied volatility. Option traders can use a currency volatility index to price options on currency pairs. Implied volatility is generally considered a measure of sentiment.

```{r, include=FALSE}
## To analyse whether the Rand is volatile lets look at Implied volatility
# What cuurencies are in the data?

cncyIV %>% group_by(Name) %>% pull(Name) %>% unique 
```

```{r}
IV_plot <- cncyIV %>% 
    
    filter(Name==c("China_IV", "India_IV", "SouthAfrica_IV",
                   "UK_IV", "EU_IV", "Singapore_IV")) %>%
    
    filter(date > as.Date("1999-12-31")) %>% 
    
    group_by(date) %>%
    
    ggplot() + 
    
    geom_line(aes(x=date, y=Price, color=Name)) +
    
    theme_bw() +  
    
    labs(x = "Dates", y = "Price (relative to USD)",
         
         title = "Implied Volatility ", subtitle = "",
         
         caption = "Note:\nOwn Calculations") +
    
    guides(col=guide_legend("Currency"))

IV_plot
```

This suggests that the market foresees the highest future volatility for the Rand, for this sub-sample.

This suggests that the market foresees the highest future volatility for the Rand [for this sub-sample].

Now I'll calculate the returns to analyse the Auto-Persistence in Returns

```{r, include=FALSE}


# Calculating Returns and Cleaning

zar_rtn <- cncy %>% 
    
    arrange(date) %>% 
    
    filter(date > as.Date("1999-12-31")) %>% 
    
    filter(Name %in% "SouthAfrica_Cncy") %>% 
    
    mutate(Price = na.locf(Price)) %>% 
    
    mutate(dlogret = log(Price) - log(lag(Price))) %>% 
    
    mutate(scaledret = (dlogret - mean(dlogret, na.rm = T))) %>% 
    
    filter(date > dplyr::first(date)) 

xts_zar_rtn <- zar_rtn %>% 
    
    tbl_xts(., cols_to_xts = "dlogret", spread_by = "Name")

MarchTest(xts_zar_rtn)
```


```{r}
xts_zar_rtn[is.na(xts_zar_rtn)] <- 0

PlotRtn = cbind(xts_zar_rtn, xts_zar_rtn^2, abs(xts_zar_rtn))

colnames(PlotRtn) = c("Returns", "Returns_Sqd", "Returns_Abs")

PlotRtn <- PlotRtn %>% 
    
    xts_tbl() %>%
    
    gather(ReturnType, Returns, -date) 

# Plot

ggplot(PlotRtn) + 
    
    geom_line(aes(x = date, y = Returns, colour = ReturnType, alpha = 0.5)) + 
    
    ggtitle("Return Type Persistence: USD/ZAR") + 
    
    facet_wrap(~ReturnType, nrow = 3, ncol = 1, scales = "free") + 
    
    guides(alpha = "none", colour = "none") + 
    
    fmxdat::theme_fmx()


```


From the graph above it is clear that there is persistence in certain periods of USDZAR returns. Moreover, we have first and second order persistence as well as clear evidence of long-term memory in the second order process.

Let's investigate further...



```{r}
forecast::Acf(xts_zar_rtn, main = "ACF: Equally Weighted Return")
```

```{r}
forecast::Acf(xts_zar_rtn^2, main = "ACF: Squared Equally Weighted Return")
```

```{r}
forecast::Acf(abs(xts_zar_rtn), main = "ACF: Absolute Equally Weighted Return")
```

```{r, include=FALSE}
Box.test(coredata(xts_zar_rtn^2), type = "Ljung-Box", lag = 12)
```



```{r, include=FALSE}

best_model <- Vol_Model_Sel(zar_rtn)

best_model
```

# Fit Model

```{r, include=FALSE}

garch_fit_gjrGARCH <- vol_func(zar_rtn, "gjrGARCH")

garch_fit_sGARCH <- vol_func(zar_rtn, "sGARCH")

signbias(garch_fit_sGARCH)
```


```{r, results = 'asis'}

pacman::p_load(xtable)

Table <- xtable(garch_fit_gjrGARCH@fit$matcoef, digits=c(0, 5, 5, 4, 4))


#print(Table, type="html")
print(Table, type = "latex", comment = FALSE)


#Conditional variance Plot

#persistence(garch_fit_sGARCH)
```

```{r}
# Persistence is alpha + beta, and it is typically very high and close to 1

# To view the conditional variance plot, use:
sigma <- sigma(garch_fit_sGARCH) %>% 
    
    xts_tbl() 

colnames(sigma) <- c("date", "sigma") 

sigma <- sigma %>% 
    
    mutate(date = as.Date(date))

Con_var_plot <- 
  
ggplot() + 
    
  geom_line(data = PlotRtn %>% filter(ReturnType == "Returns_Sqd") %>% 
                
                select(date, Returns) %>% 
              
              unique %>% mutate(Returns = sqrt(Returns)), 
            
            aes(x = date, y = Returns)) + 
  
  geom_line(data = sigma, aes(x = date, y = sigma), 
            color = "red", size = 2, alpha = 0.8) + 
  
  
  labs(title = "Comparison: Returns Sigma vs Sigma from Garch", 
       
       subtitle = "Note the smoothing effect of garch, as noise is controlled for.", x = "", y = "Comparison of estimated volatility",
       
       caption = "Source: Fin metrics class | Calculations: Own") + 
  
    fmxdat::theme_fmx(CustomCaption = TRUE)


fmxdat::finplot(Con_var_plot, y.pct = T, y.pct_acc = 1)

```

```{r}
news_plot <- newsimpact(z = NULL, garch_fit_sGARCH)

plot(news_plot$zx, news_plot$zy, ylab = news_plot$yexpr, xlab = news_plot$xexpr, type = "l", 
    main = "News Impact Curve")
```

```{r}

plot(garch_fit_sGARCH, which = "all")
```

Lets investigate further by compare smoothed ZAR Volatility to mean Global volatility


```{r}
# Lets investigate further
# lets compare Smoothed ZAR Vol to mean Global VOL

# Calculate Mean Global VOL

mean_Gvol <- cncyIV %>% 
    
    filter(date > as.Date("1999-12-31")) %>% 
    
    group_by(date) %>% 
    
    summarise(mean_vol = mean(Price)) %>% 
    
    mutate(Global_vol = mean_vol/max(mean_vol))

# Wrangle Sigma 

sigma <- sigma %>% 
    
    mutate(Date = as.Date(date)) %>% 
    
    mutate(ZAR_sigma = sigma/max(sigma))%>%
    
    left_join(., mean_Gvol, by = "date")

# Plot 

Vol_compare_plot <- sigma %>% 
    
    select(-date) %>% 
    
    pivot_longer(c("ZAR_sigma", "Global_vol"), 
                 names_to = "Vol_type", 
                 values_to = "VOL") %>%
    
    ggplot() +
    
    geom_line(aes(Date, VOL, colour = Vol_type)) +
    
    labs(title = "ZAR Volatility and Mean Currency Volatility",
         x = "", 
         y = "Proprotion of Max Vol") +
    
    fmx_cols() +
    
    theme_fmx(title.size = ggpts(25)) 

finplot(Vol_compare_plot)

```



















\newpage

# References {-}

<div id="refs"></div>


# Appendix {-}

## Appendix A {-}

Some appendix information here

## Appendix B {-}

