---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Helping You Write Academic Papers in R using Texevier"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Nico Katzke^[__Contributions:__  \\newline _The authors would like to thank no institution for money donated to this project. Thank you sincerely._]"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Prescient Securities, Cape Town, South Africa" # First Author's Affiliation
Email1: "nfkatzke\\@gmail.com" # First Author's Email address

Author2: "John Smith"
Ref2: "Some other Institution, Cape Town, South Africa"
Email2: "John\\@gmail.com"
CommonAffiliation_12: TRUE # If Author 1 and 2 have a common affiliation. Works with _13, _23, etc.

Author3: "John Doe"
Email3: "Joe\\@gmail.com"

CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  Abstract to be written here. The abstract should not be too long and should provide the reader with a good understanding what you are writing about. Academic papers are not like novels where you keep the reader in suspense. To be effective in getting others to read your paper, be as open and concise about your findings here as possible. Ideally, upon reading your abstract, the reader should feel he / she must read your paper in entirety.
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')

if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

list.files('C:/Users/Cabous/OneDrive/Desktop/22017542_Exam/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```


```{r}
# Load Data
pacman::p_load("MTS", "robustbase")
pacman::p_load("tidyverse", "devtools", "rugarch", "rmgarch", 
    "forecast", "tbl2xts", "lubridate", "PerformanceAnalytics", 
    "ggthemes", "fmxdat", "cowplot")

msci <- read_rds("data/msci.rds")
bonds <- read_rds("data/bonds_10y.rds")
comms <- read_rds("data/comms.rds")
```


```{r, include=FALSE}
# Calculate Returns for Assets

# 1. First Calculate Returns for MSCI All Country World Index
# For last decade

Equities <- msci %>%
    
    group_by(Name) %>% 
    
    filter(Name %in% "MSCI_ACWI") %>% 
    
    mutate(dlogret = log(Price) - log(lag(Price))) %>%
    
    mutate(scaledret = (dlogret - mean(dlogret, na.rm = T))) %>% 
    
    filter(date > dplyr::first(date)) %>% 
    
    select(-Price) %>%
    
    filter(date > as.Date("2009-12-31")) %>% 
    
    rename(MSCI_ACWI = scaledret) %>%
    
    select(date, MSCI_ACWI)

# 2. Calculate US 10 Year Bond Returns

US_bond <- bonds %>%
    
    group_by(Name) %>%
    
    filter(Name %in% "US_10Yr") %>% 
    
    mutate(dlogret = Bond_10Yr/lag(Bond_10Yr) - 1) %>%
    
    mutate(scaledret = (dlogret - mean(dlogret, na.rm = T))) %>% 
    
    filter(date > dplyr::first(date)) %>% 
    
    select(-Bond_10Yr) %>%
    
    filter(date > as.Date("2009-12-31"))%>%
    
    rename(US_10Yr = scaledret) %>%
    
    select(date, US_10Yr)

# 3. Calculate Global Real Estate Returns

Real_Estate <- msci %>% 
    
    group_by(Name) %>%
    
    filter(Name %in% "MSCI_RE") %>% 
    
    mutate(dlogret = log(Price) - log(lag(Price))) %>% 
    
    mutate(scaledret = (dlogret - mean(dlogret, na.rm = T))) %>% 
    
    filter(date > dplyr::first(date)) %>% 
    
    select(-Price) %>%
    
    filter(date > as.Date("2009-12-31")) %>% 
    
    rename(MSCI_RE = scaledret) %>%
    
    select(date, MSCI_RE)

# 4. Calculate Oil Returns

Oil <- comms %>% 
    
    group_by(Name) %>%
    
    filter(Name %in% "Oil_Brent" ) %>% 
    
    mutate(dlogret = log(Price) - log(lag(Price))) %>% 
    
    mutate(scaledret = (dlogret - mean(dlogret, na.rm = T))) %>% 
    
    filter(date > dplyr::first(date)) %>%
    
    select(-Price) %>%
    
    filter(date > as.Date("2009-12-31")) %>%
    
    rename(Oil_Brent = scaledret) %>%
    
    select(date, Oil_Brent)

# Combine and wrangle for DCC models

asset_classes_ret <- left_join(Equities, US_bond, by = c("date")) %>% 
    
    left_join(., Real_Estate, by = c("date")) %>% 
    
    left_join(., Oil, by = c("date")) %>% 
    
    tbl_xts()

```


```{r}
# Lets test for autocorrelation using the March Test

MarchTest(asset_classes_ret)
```
The MARCH test indicates that all the MV portmanteau tests reject the null of no conditional heteroskedasticity, motivating our use of MVGARCH models. Let's set up the model

```{r}
# GARCH specifications

uspec <- ugarchspec(variance.model = list(model = "gjrGARCH", 
    garchOrder = c(1, 1)), mean.model = list(armaOrder = c(1, 
    0), include.mean = TRUE), distribution.model = "sstd")

multi_univ_garch_spec <- multispec(replicate(ncol(asset_classes_ret), uspec))

# DCC specifications

spec.dcc = dccspec(multi_univ_garch_spec, dccOrder = c(1, 1), 
    distribution = "mvnorm", lag.criterion = c("AIC", "HQ", "SC", 
        "FPE")[1], model = c("DCC", "aDCC")[1])  

# Enable clustering for speed:

cl = makePSOCKcluster(10)

# Fit GARCH

multf = multifit(multi_univ_garch_spec, asset_classes_ret, cluster = cl)

# Fit DCC

fit.dcc = dccfit(spec.dcc, data = asset_classes_ret, solver = "solnp", 
    cluster = cl, fit.control = list(eval.se = FALSE), fit = multf)

# Check Model

RcovList <- rcov(fit.dcc)

covmat = matrix(RcovList, nrow(asset_classes_ret), ncol(asset_classes_ret) * ncol(asset_classes_ret), 
    byrow = TRUE)

mc1 = MCHdiag(asset_classes_ret, covmat)

```

```{r}
# Wrangle output
dcc.time.var.cor <- rcor(fit.dcc)
print(dcc.time.var.cor[, , 1:3])

dcc.time.var.cor <- aperm(dcc.time.var.cor, c(3, 2, 1))
dim(dcc.time.var.cor) <- c(nrow(dcc.time.var.cor), ncol(dcc.time.var.cor)^2)
```

```{r}
# Rename Output

dcc.time.var.cor <- renamingdcc(ReturnSeries = asset_classes_ret, DCC.TV.Cor = dcc.time.var.cor)

# Now we can plot ;)

# Equities

DCC_eq_plot <- ggplot(dcc.time.var.cor %>% 
                          
                          filter(grepl("MSCI_ACWI_", Pairs), 
                                 !grepl("_MSCI_ACWI", Pairs))) + 
    
    geom_line(aes(x = date, y = Rho, colour = Pairs)) + 
    
    theme_hc() + labs(subtitle = "Dynamic Conditional Correlations: MSCI_ACWI", x = "", y = "") +
    
    fmx_cols() + 
    
    theme_fmx(subtitle.size = ggpts(25), legend.size = ggpts(15))


# US Bonds
DCC_bond_plot <- ggplot(dcc.time.var.cor %>% 
                            
                            filter(grepl("US_10Yr_", Pairs), 
                                   !grepl("_US_10Yr", Pairs))) + 
    
    geom_line(aes(x = date, y = Rho, colour = Pairs)) + theme_hc() + 
    
    labs(subtitle="Dynamic Conditional Correlations: US_10Yr", x = "", y = "") +
    
    fmx_cols() + 
    
    theme_fmx(subtitle.size = ggpts(25), legend.size = ggpts(15))


# Real Estate

DCC_RE_plot <- ggplot(dcc.time.var.cor %>% 
                          
                          filter(grepl("MSCI_RE_", Pairs), 
                                 !grepl("_MSCI_RE", Pairs))) + 
    
    geom_line(aes(x = date, y = Rho, colour = Pairs)) + theme_hc() + 
    
    labs(subtitle = "Dynamic Conditional Correlations: MSCI_RE", x = "", y = "") +
    
    fmx_cols() + 
    
    theme_fmx(subtitle.size = ggpts(25), legend.size = ggpts(15))



# Oil

DCC_oil_plot <- ggplot(dcc.time.var.cor %>% 
                           
                           filter(grepl("Oil_Brent_", Pairs), 
                                  !grepl("_Oil_Brent", Pairs))) +
    
    geom_line(aes(x = date, y = Rho, colour = Pairs)) + 
    
    theme_hc() + 
    
    labs(subtitle = "Dynamic Conditional Correlations: Oil_Brent", x = "", y = "") +
    
    fmx_cols() + 
    
    theme_fmx(subtitle.size = ggpts(25), legend.size = ggpts(15))


```


```{r}
plot_grid(DCC_eq_plot, DCC_bond_plot, DCC_RE_plot , DCC_oil_plot, labels = c('', '', '',''))
```


# Go Garch

```{r}
# Go-GARCH following the Tutorial

# GARCH Specifications
spec.go <- gogarchspec(multi_univ_garch_spec, 
                       distribution.model = 'mvnorm', 
                       ica = 'fastica') 

# Speed:

cl <- makePSOCKcluster(10)

# Fit GARCH

multf <- multifit(multi_univ_garch_spec, asset_classes_ret, cluster = cl)

#GO-GARCH Specifications

fit.gogarch <- gogarchfit(spec.go, 
                      data = asset_classes_ret, 
                      solver = 'hybrid', 
                      cluster = cl, 
                      gfun = 'tanh', 
                      maxiter1 = 40000, 
                      epsilon = 1e-08, 
                      rseed = 100)

# Go-Garch Fit

print(fit.gogarch)

```


```{r}

# Wrangle Output

gog.time.var.cor <- rcor(fit.gogarch)

gog.time.var.cor <- aperm(gog.time.var.cor,c(3,2,1))

dim(gog.time.var.cor) <- c(nrow(gog.time.var.cor), ncol(gog.time.var.cor)^2)

# Rename Output

gog.time.var.cor <- renamingdcc(ReturnSeries = asset_classes_ret, DCC.TV.Cor = gog.time.var.cor)


# Plots

# Equities

GO_eq_plot <- ggplot(gog.time.var.cor %>% 
                   
                   filter(grepl("MSCI_ACWI_", Pairs), 
                          !grepl("_MSCI_ACWI", Pairs))) + 
    
    geom_line(aes(x = date, y = Rho, colour = Pairs)) +
    
    theme_hc() + 
    
    labs(subtitle = "Go-Garch: MSCI_ACWI", x = "", y = "") +
    
    fmx_cols() + 
    
    theme_fmx(subtitle.size = ggpts(25), legend.size = ggpts(15))

# Bonds

GO_bond_plot <- ggplot(gog.time.var.cor %>% 
                   
                   filter(grepl("US_10Yr_", Pairs), !grepl("_US_10Yr", Pairs))) +
    
    geom_line(aes(x = date, y = Rho, colour = Pairs)) + 
    
    theme_hc() + 
    
    labs(subtitle="Go-Garch: US_10Yr", x = "", y = "") +
    
    fmx_cols() + 
    
    theme_fmx(subtitle.size = ggpts(25), legend.size = ggpts(15))

# Real Estate

GO_RE_plot <- ggplot(gog.time.var.cor %>%
                   
                   filter(grepl("MSCI_RE_", Pairs), !grepl("_MSCI_RE", Pairs))) +
    
    geom_line(aes(x = date, y = Rho, colour = Pairs)) + 
    
    theme_hc() +
    
    labs(subtitle = "Go-Garch: MSCI_RE", x = "", y = "") +
    
    fmx_cols() +
    
    theme_fmx(subtitle.size = ggpts(25), legend.size = ggpts(15))


# Commodities

GO_oil_plot <- ggplot(gog.time.var.cor %>%
                   
                   filter(grepl("Oil_Brent_", Pairs), !grepl("_Oil_Brent", Pairs))) + 
    
    geom_line(aes(x = date, y = Rho, colour = Pairs)) + 
    
    theme_hc() + 
    
    labs(subtitle = "Go-GARCH: Oil_Brent", x = "", y = "") +
    
    fmx_cols() + 
    
    theme_fmx(subtitle.size = ggpts(25), legend.size = ggpts(15))


```


```{r}
plot_grid(GO_eq_plot, GO_bond_plot, GO_RE_plot , GO_oil_plot, labels = c('', '', '',''))

```


```{r}
library(factoextra)
library(FactoMineR)
pacman::p_load("psych")

eq_pca <- msci %>% 
    
    spread(Name, Price) %>% 
    
    select(date, MSCI_ACWI)

bond_pca <- bonds %>% 
    
    spread(Name, Bond_10Yr) %>% 
    
    select(date, US_10Yr)

Re_pca <- msci %>% 
    
    spread(Name, Price) %>% 
    
    select(date, MSCI_RE)
    
oil_pca <- comms %>%  
    
    spread(Name, Price) %>% 
    
    select(date, Oil_Brent)

# Combine

asset_class_pca <- left_join(eq_pca, bond_pca, by = c("date")) %>% 
    
    left_join(., Re_pca, by = c("date")) %>% 
    
    left_join(., oil_pca, by = c("date")) %>% 
    
    gather(Tickers, Price, -date) %>%
    
    group_by(Tickers) %>%
    
    filter(date > as.Date("2009-12-31")) %>% 
    
    arrange(date) %>%  
    
    group_by(Tickers) %>%  
    
    mutate(dlogret = log(Price) - log(lag(Price))) %>% 
    
    mutate(scaledret = (dlogret -  mean(dlogret, na.rm = T))) %>% 
    
    filter(date > dplyr::first(date)) %>% 
    
    ungroup()


asset_classes_pca <- asset_class_pca %>%  
    
    select(date, Tickers, dlogret) %>% 
    
    spread(Tickers, dlogret) %>% 
    
    select(-date)

AC_PCA_plot <- prcomp(asset_classes_pca, center = TRUE, scale. = TRUE)

AC_PCA_plot$rotation

pairs.panels(asset_classes_pca)

```


```{r}
gviolion <- asset_classes_pca %>% 
    
    gather(Type, val) %>% 
    
    ggplot() + 
    
    geom_violin(aes(Type, val, fill = Type), alpha = 0.7) +
    
    fmxdat::theme_fmx() + 
    
    fmxdat::fmx_fills()

fmxdat::finplot(gviolion, y.pct = T, y.pct_acc = 1, x.vert = T)

```


The US 10 year bond shows the highest degree of dispersion, followed by Oil, and clearly follows a different distribution process to the other two indices.






\newpage

# References {-}

<div id="refs"></div>


# Appendix {-}

## Appendix A {-}

Some appendix information here

## Appendix B {-}

