---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

#title: "Question 2: Yield Spread"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: yes
Entry1: Question 3 -  Portfolio Construction
Entry2: \textbf{Carel Olivier} # textbf for bold
Entry3: 22017542
#Uni_Logo: Tex/yield curve.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
#Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
#AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
#Author1: "Carel Olivier"  # First Author - note the thanks message displayed as an italic footnote of first page.
#Ref1: "22017542" # First Author's Affiliation
#Email1: "nfkatzke\\@gmail.com" # First Author's Email address

# Comment out below to remove both. JEL Codes only given if keywords also given.
#keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
#JELCodes: "L250 \\sep L100"

CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |

---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
library(lubridate)
library(tbl2xts)
library(fmxdat)
library(cowplot)
library(zoo)
list.files('C:/Users/Cabous/OneDrive/Desktop/22017542_Exam/Questions/Question3/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```


# Short Introduction

Firstly I will compare the SWIX and ALSI by looking at the performance of different size indexes (large and small caps). I did not include Mid Caps since the graphs did not make sense. 

```{r}

T40 <- read_rds("data/T40.rds")

RebDays <- read_rds("data/Rebalance_days.rds")

```



```{r}
# First: calculate ordinary returns
library(lubridate)

#------------------ 
# Step one: gather to make tidy:
 
# lets try: large caps J200

# First the weights:

W_xts_L200 <- T40 %>% 
    
    arrange(date) %>% 
    
    select(date, Tickers, Return, Index_Name, J200) %>% 
    
    #mutate(J200 = J200*Return) %>% 
    
    filter(date >= as.Date("2010/01/01")) %>% 
    
    filter(Index_Name == "Large_Caps") %>% 
    
    filter(date == first(date)) %>%
    
    mutate(weight = 1/n()) %>% 
    
    tbl_xts(., cols_to_xts = weight, spread_by = Tickers)

# Now Returns:
R_xts_L200 <- T40 %>% 
    
    arrange(date) %>% 
    
    select(date, Tickers, Return, Index_Name, J200) %>%
    
    #mutate(J200 = J200*Return) %>% 
    
    filter(date >= as.Date("2010/01/01")) %>% 
    
    filter(Index_Name == "Large_Caps") %>% 
    
    tbl_xts(., cols_to_xts = Return, spread_by = Tickers)

# Now... first ensure that column names between R_xts and
# W_xts match:

R_xts_L200 <- R_xts_L200[, names(W_xts_L200)]

# Set all NA returns to zero:

R_xts_L200[is.na(R_xts_L200)] <- 0

# Set all NA weights to zero:

W_xts_L200[is.na(W_xts_L200)] <- 0

# Also set NA's to zero:

Portfolio_L200 <- rmsfuns::Safe_Return.portfolio(R = R_xts_L200, weights = W_xts_L200, 
                                            geometric = TRUE)

Portf_Rets_L200 <- Portfolio_L200$portfolio.returns %>% xts_tbl() 

# Now large caps J400

# First the weights:

W_xts_L400 <- T40 %>% 
    
    arrange(date) %>% 
    
    select(date, Tickers, Return, Index_Name, J400) %>% 
    
    filter(date >= as.Date("2010/01/01")) %>% 
    
    #mutate(Return = coalesce(Return, 0)) %>% 
    
   # mutate(J400 = J400*Return) %>%
    
    filter(Index_Name == "Large_Caps") %>% 
    
    filter(date == first(date)) %>%
    
    mutate(weight = 1/n()) %>% 
    
    tbl_xts(., cols_to_xts = weight, spread_by = Tickers)

# Now Returns:
R_xts_L400 <- T40 %>% 
    
    arrange(date) %>% 
    
    select(date, Tickers, Return, Index_Name, J400) %>% 
    
    filter(date >= as.Date("2010/01/01")) %>% 
    
    filter(Index_Name == "Large_Caps") %>% 
    
    tbl_xts(., cols_to_xts = Return, spread_by = Tickers)

# Now... first ensure that column names between R_xts and
# W_xts match:

R_xts_L400 <- R_xts_L400[, names(W_xts_L400)]

# Set all NA returns to zero:

R_xts_L400[is.na(R_xts_L400)] <- 0

# Set all NA weights to zero:

W_xts_L400[is.na(W_xts_L400)] <- 0

# Also set NA's to zero:

Portfolio_L400 <- rmsfuns::Safe_Return.portfolio(R = R_xts_L400, weights = W_xts_L400, 
                                            geometric = TRUE)

Portf_Rets_L400 <- Portfolio_L400$portfolio.returns %>% xts_tbl()

# Join L200 and L400 to plot

Portf_Rets_L200 <- Portf_Rets_L200 %>% mutate(Index = "J200") 
    
Portf_Rets_L400 <- Portf_Rets_L400 %>% mutate(Index = "J400") 

# combine

Portf_Rets_L <- rbind.data.frame(Portf_Rets_L200, Portf_Rets_L400)

# Plot
Portf_Rets_L %>% 
    
    arrange(date) %>% 
    
# Set NA Rets to zero to make cumprod work:
#mutate(Rets = coalesce(ret, 0)) %>% 
    
    mutate(CP = cumprod(1 + portfolio.returns)) %>% 
    
    ungroup() %>% 
    
   # arrange(date) %>% 
    
    ggplot() +
    
    geom_line(aes(date, CP, color = Index), alpha = 0.8) +
    
    labs(title = "Cumulative Returns per Index for ALSI and SWIX",
         subtitle = "Large Caps",
         y = "Cumulative Returns", x ="") +
    
    fmxdat::theme_fmx(title.size = ggpts(30), subtitle.size = ggpts(25), legend.size = ggpts(20))


```

# Small-Caps

```{r}
# Mid-Caps

W_xts_M200 <- T40 %>% 
    
    arrange(date) %>% 
    
    select(date, Tickers, Return, Index_Name, J200) %>% 
    
    #mutate(J200 = J200*Return) %>% 
    
    filter(date >= as.Date("2008/01/01")) %>% 
    
    filter(Index_Name == "Small_Caps") %>% 
    
    filter(date == first(date)) %>%
    
    mutate(weight = 1/n()) %>% 
    
    tbl_xts(., cols_to_xts = weight, spread_by = Tickers)

# Now Returns:
R_xts_M200 <- T40 %>% 
    
    arrange(date) %>% 
    
    select(date, Tickers, Return, Index_Name, J200) %>%
    
    filter(date >= as.Date("2008/01/01")) %>% 
    
    filter(Index_Name == "Small_Caps") %>%
    
    na.locf(.,na.rm=T, 10) %>%
    
    tbl_xts(., cols_to_xts = Return, spread_by = Tickers)

# Now... first ensure that column names between R_xts and
# W_xts match:

R_xts_M200 <- R_xts_M200[, names(W_xts_M200)]

# Set all NA returns to zero:

R_xts_M200[is.na(R_xts_M200)] <- 0

# Set all NA weights to zero:

W_xts_M200[is.na(W_xts_M200)] <- 0

# Also set NA's to zero:

Portfolio_M200 <- rmsfuns::Safe_Return.portfolio(R = R_xts_M200, weights = W_xts_M200, 
                                            geometric = TRUE)

Portf_Rets_M200 <- Portfolio_M200$portfolio.returns %>% xts_tbl() 

# Now large caps J400

# First the weights:

W_xts_M400 <- T40 %>% 
    
    arrange(date) %>% 
    
    select(date, Tickers, Return, Index_Name, J400) %>% 
    
    filter(date >= as.Date("2008/01/01")) %>% 
    
    #mutate(Return = coalesce(Return, 0)) %>% 
    
   # mutate(J400 = J400*Return) %>%
    
    filter(Index_Name == "Small_Caps") %>% 
    
    filter(date == first(date)) %>%
    
    mutate(weight = 1/n()) %>% 
    
    tbl_xts(., cols_to_xts = weight, spread_by = Tickers)

# Now Returns:
R_xts_M400 <- T40 %>% 
    
    arrange(date) %>% 
    
    select(date, Tickers, Return, Index_Name, J400) %>% 
    
    filter(date >= as.Date("2008/01/01")) %>% 
    
    filter(Index_Name == "Small_Caps") %>%
    
    na.locf(.,na.rm=T, 10) %>% 
    
    tbl_xts(., cols_to_xts = Return, spread_by = Tickers)

# Now... first ensure that column names between R_xts and
# W_xts match:

R_xts_M400 <- R_xts_M400[, names(W_xts_M400)]

# Set all NA returns to zero:

R_xts_M400[is.na(R_xts_M400)] <- 0

# Set all NA weights to zero:

W_xts_M400[is.na(W_xts_M400)] <- 0

# Also set NA's to zero:

Portfolio_M400 <- rmsfuns::Safe_Return.portfolio(R = R_xts_M400, weights = W_xts_M400, 
                                            geometric = TRUE)

Portf_Rets_M400 <- Portfolio_M400$portfolio.returns %>% xts_tbl()

# Join L200 and L400 to plot

Portf_Rets_M200 <- Portf_Rets_M200 %>% mutate(Index = "J200") 
    
Portf_Rets_M400 <- Portf_Rets_M400 %>% mutate(Index = "J400") 

# combine

Portf_Rets_M <- rbind.data.frame(Portf_Rets_M200, Portf_Rets_M400)

# Plot
Portf_Rets_M %>% 
    
    arrange(date) %>% 
    
# Set NA Rets to zero to make cumprod work:
#mutate(Rets = coalesce(ret, 0)) %>% 
    
    mutate(CP = cumprod(1 + portfolio.returns)) %>% 
    
    ungroup() %>% 
    
   # arrange(date) %>% 
    
    ggplot() +
    
    geom_line(aes(date, CP, color = Index), alpha = 0.8)+
    labs(title = "Cumulative Returns per Index for ALSI and SWIX",
         subtitle = "Small Caps",
         y = "Cumulative Returns", x ="") +
    
    fmxdat::theme_fmx(title.size = ggpts(30), subtitle.size = ggpts(25), legend.size = ggpts(20))


```

\newpage

# Capped Portfolio 

To answer the JSE’s question on applying capping to the indexes I will be looking at the impact different capping levels would have had on both the SWIX and ALSI (6% and 10%).

```{r}
# Construct Capped Portfolio and Determine Performance for ALSI

reb_ALSI <- T40 %>% 
    
    filter(date %in% RebDays$date) %>% 
    
# Now we have to distinguish rebalances - to create something
# to group by:
    
    mutate(RebalanceTime = format(date, "%Y%B")) %>% 
    
    select(date, Tickers, Return, J200, RebalanceTime) %>% 
    
    rename(weight = J200) %>% 
    
    mutate(weight = coalesce(weight , 0))
  
# Apply Proportional_Cap_Foo to ALSI to get capped return for cap of 10%

Capped_df <- reb_ALSI %>% 
    
    group_split(RebalanceTime) %>% 
    
    map_df(~Proportional_Cap_Foo(., W_Cap = 0.1) ) %>% 
    
    select(-RebalanceTime)
 

ALSI_wts <- Capped_df %>% 
    
    tbl_xts(cols_to_xts = weight, spread_by = Tickers)


ALSI_rts <- T40 %>% 
    
    filter(Tickers %in% unique(Capped_df$Tickers)) %>% 
    
    tbl_xts(cols_to_xts = Return, spread_by = Tickers)


ALSI_wts[is.na(ALSI_wts)] <- 0

ALSI_rts[is.na(ALSI_rts)] <- 0


ALSI_capped <- rmsfuns::Safe_Return.portfolio(R = ALSI_rts, weights = ALSI_wts, 
    lag_weights = T) %>% 
    
    xts_tbl() %>% 
    
    rename(ALSI = portfolio.returns)

# Construct Capped Portfolio and Determine Performance for SWIX

reb_SWIX <- T40 %>% 
    
    filter(date %in% RebDays$date) %>%
    
    mutate(RebalanceTime = format(date, "%Y%B")) %>%
    
    select(date, Tickers, Return, J400, RebalanceTime) %>% 
    
    rename(weight = J400) %>% 
    
    mutate(weight = coalesce(weight , 0))
  
# Apply Proportional_Cap_Foo to ALSI to get capped return for cap of 6%

Capped_df <- reb_SWIX %>% 
    
    group_split(RebalanceTime) %>% 
    
    map_df(~Proportional_Cap_Foo(., W_Cap = 0.06) ) %>% 
    
    select(-RebalanceTime)
 

SWIX_wts <- Capped_df %>% 
    
    tbl_xts(cols_to_xts = weight, spread_by = Tickers)


SWIX_rts <- T40 %>% 
    
    filter(Tickers %in% unique(Capped_df$Tickers)) %>%
    
    tbl_xts(cols_to_xts = Return, spread_by = Tickers)


SWIX_wts[is.na(SWIX_wts)] <- 0

SWIX_rts[is.na(SWIX_rts)] <- 0


SWIX_capped <- rmsfuns::Safe_Return.portfolio(R = SWIX_rts, weights = SWIX_wts, 
    lag_weights = T) %>% 
    
    xts_tbl() %>% 
    
rename(SWIX = portfolio.returns)


# Combine and Plot Performance

capped_indices <- left_join(ALSI_capped, SWIX_capped, by = "date") %>% 
    
    pivot_longer(c("ALSI", "SWIX"), names_to = "Meth", values_to = "returns")
```


```{r}

# Apply Proportional_Cap_Foo to ALSI to get capped return for cap of 6%

Capped_df_6p <- reb_ALSI %>% 
    
    group_split(RebalanceTime) %>% 
    
    map_df(~Proportional_Cap_Foo(., W_Cap = 0.06) ) %>% 
    
    select(-RebalanceTime)
 

ALSI_wts_6p <- Capped_df_6p %>% 
    
    tbl_xts(cols_to_xts = weight, spread_by = Tickers)


ALSI_rts_6p <- T40 %>% 
    
    filter(Tickers %in% unique(Capped_df_6p$Tickers)) %>% 
    
    tbl_xts(cols_to_xts = Return, spread_by = Tickers)


ALSI_wts_6p[is.na(ALSI_wts_6p)] <- 0

ALSI_rts_6p[is.na(ALSI_rts_6p)] <- 0


ALSI_capped_6p <- rmsfuns::Safe_Return.portfolio(R = ALSI_rts_6p, weights = ALSI_wts_6p, 
    lag_weights = T) %>% 
    
    xts_tbl() %>% 
    
    rename(ALSI = portfolio.returns)

# Apply Proportional_Cap_Foo to SwIX to get capped return for cap of 10%

Capped_df_10p <- reb_SWIX %>% 
    
    group_split(RebalanceTime) %>% 
    
    map_df(~Proportional_Cap_Foo(., W_Cap = 0.1) ) %>% 
    
    select(-RebalanceTime)
 

SWIX_wts_10p <- Capped_df_10p %>% 
    
    tbl_xts(cols_to_xts = weight, spread_by = Tickers)


SWIX_rts_10p <- T40 %>% 
    
    filter(Tickers %in% unique(Capped_df_10p$Tickers)) %>%
    
    tbl_xts(cols_to_xts = Return, spread_by = Tickers)


SWIX_wts_10p[is.na(SWIX_wts_10p)] <- 0

SWIX_rts_10p[is.na(SWIX_rts_10p)] <- 0


SWIX_capped_10p <- rmsfuns::Safe_Return.portfolio(R = SWIX_rts_10p, weights = SWIX_wts_10p, 
    lag_weights = T) %>% 
    
    xts_tbl() %>% 
    
rename(SWIX = portfolio.returns)


# Combine and Plot Performance

capped_indices_6p <- left_join(ALSI_capped_6p, SWIX_capped_10p, by = "date") %>% 
    
    pivot_longer(c("ALSI", "SWIX"), names_to = "Meth", values_to = "returns")



ALSI_SWIX_6p <- left_join(ALSI_capped_6p, SWIX_capped_10p, by = "date") %>% 
    
    pivot_longer(c("ALSI", "SWIX"), names_to = "Meth", values_to = "Returns")


q2_p3_6p <- capped_indices_6p %>% 
    
    group_by(Meth) %>%
    
    mutate(Idx = cumprod(1 + returns)) %>% 
    
ggplot() + 
    
geom_line(aes(date, Idx, colour = Meth), alpha = 0.8) + 
    
labs(subtitle = "ALSI capped at 6% and SWIX at 10%", 
    x = "", y = "Cumulative Return") +
    
    fmx_cols() + 
    
fmxdat::theme_fmx(subtitle.size = ggpts(20))


q2_p3 <- capped_indices %>% 
    
    group_by(Meth) %>%
    
    mutate(Idx = cumprod(1 + returns)) %>% 
    
ggplot() + 
    
geom_line(aes(date, Idx, colour = Meth), alpha = 0.8) + 
    
labs(subtitle = "ALSI capped at 10% and SWIX at 6%", 
    x = "", y = "Cumulative Return") +
    
    fmx_cols() + 
    
fmxdat::theme_fmx(subtitle.size = ggpts(20))

plot_grid(finplot(q2_p3), finplot(q2_p3_6p), labels = list(title = "Comparing Capped returns of ALSI and SWIX"), label_size = ggpts(30), align = "h")
```



